\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 appendix.tex

Plan of action:
---------------------------------------------

- What is the paper saying/should be saying?
- Simplify notations....pwa relational and k-relational

- Modify ordering of sections: Abstraction -> PWA enrichment
- Simplify notations
- Fold multiple PWA relational/transitions system into one and use the
  transitions system as a semantic interpretation for model checking.
  Can be eliminated if automatons/kripke structures are used instead.
- Fix the `convex-hull' in the definition 2.2 PWA Relational Model.
  Showcase clustering using a benchmark. Add it to future work
  and cite Nimit's  paper. Or, retract it entirely?
- Clearly state that the approach is not a generic data-drive system
  identification technique, but focused on the falsification aspect.
  We only model selective state-space regions: abstract violations.
- De-emphasize OLS (and the process and the cost functions used for
  modeling). Add that the idea hinges on selectively identifying the
  state-space for modeling and not how the models might be created.
  Emphasize again that the requirement is only on the linearity of
  the individual models and hence, OLS is one way. Trade-off between
  efficiency and complexity can be achieved by selecting the `right'
  modeling template.
- Add benchmarks: hybrid with multiple modes.

Summary of the reviews
---------------------------------------------

R1: Like the idea but the presentation and results need improvement

- Clarify that the plant is inherently a hybrid dynamical system
  and in the future (or if time permits) a controller can be added and
  analyzed together as a infinite state transition system.
- Clarify the clustering done.

R2: Seems the most positive, but focuses on PWA identification.

- Clarify the purpose of the approach is to use sub-optimal
  identification techniques but still provide a `reasonable' and
  scalable falsification technique.

R3: Poor benchmarks: use automotive control examples, try
polynomial kernels (with Z3), compare with simulation based
falsification (S-Taliro?).

- Try polynomial kernels on a benchmark?
- Clarify S3CAM was already compared with S-Taliro.

R4: Probably the most negative review.
Sloppy presentation; high level concepts are not well presented
and contributions are not clear. Benchmarks are too simple. Why OLS?
Contributions are not significant/novel.

- Spell out the contributions clearly.
- Use Simulink models.
- Cite papers which learn hybrid automata from i/o traces, and clarify
  the difference.
  \cite{medhat2015framework} and many others
- Clarify that OLS is just one choice out of many.

R5: Probably a borderline.

- Add a motivation section showcasing the contributions.

--
============================================================================
EMSOFT 2017 Reviews for Submission 159
============================================================================

>>>>

============================================================================
EMSOFT 2017 Reviews for Submission 159
============================================================================
